Analyzing and Comparing Income Inequality Trends in the Canada: Impacts of the Great Recession and COVID-19 Pandemic

### 2024-11-28 paper/paper.qmd
Update paper.qmd

This paper aims to investigate the dynamics of income inequality in the United States, especially focusing on the period from 2002 to 2019. Using the dataset provided by United States Census and World Inequality Database (WID), we will fully investigate income trends across the social class, top 1%, top 10% and bottom 50% of income inequality. Moreover, will be considering variables such as year, social class, and race to find out the correlation between these factors.

>>>>

This paper aims to investigate the dynamics of income inequality in Canada, especially focusing on the period from 2002 to 2023. Using the dataset provided by the World Inequality Database (WID), the paper will fully investigate income trends across the social class, top 1%, top 10% and bottom 50% of income inequality. Moreover, will be considering variables such as year, social class, and race to find out the correlation between these factors.
